---
title: "Livesession4assignment"
author: "Jeff Weltman"
date: "September 21, 2017"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1 - FiveThirtyEight Data
### *Install the fivethirtyeight package*

```{r Install fivethirtyeight package, echo=TRUE}
install.packages("fivethirtyeight", repos="http://cran.us.r-project.org")
```

### *In the listing of data sets, assign the eighteeenth data set to an object 'df'.*

```{r Assigning Data Set, echo=TRUE}
data(package = "fivethirtyeight")
df <- fivethirtyeight::college_recent_grads
browseVignettes(package = "fivethirtyeight")
# URL http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/
```

### *Give the dimensions and column names of this data frame.*
```{r Dimensions and Column Names, echo=TRUE}
dim(df)
colnames(df)
```
***
# Question 2 - Data Summary
### *Write an R command that gives you the column names of the data frame, then countst he number of columns **but not** rows.*
```{r Column names and numbers, echo=TRUE}
colnames(df)
length(colnames(df))
```

### *Generate a count of each unique major_category.*
```{r Major Count, echo=TRUE}
install.packages("sqldf", repos="http://cran.us.r-project.org")
library(sqldf)
major_count <- sqldf("select distinct(major_category) as MajorCategory, count(major_category) as MajorCount from df group by major_category")
major_count
```

### *Create a bar plot of major_count.*
```{r Bar Plot of major_count}
par(mai=c(1,2.5,1,1))
barplot(height=major_count$MajorCount,space=0.08,cex.names=.7,names.arg=c(major_count$MajorCategory),las=2,horiz=TRUE,col="Purple",xlab="Majors per Category",main="Count of Recent College Majors")
```

### *Output the fivethirtyeight data as a .csv without row names.*
```{r Output CSV, echo=TRUE}
write.csv(file=paste(getwd(),"/msds/6306/unit4/fivethirtyeight.csv", sep=""), x=major_count, row.names=F)
```
***
# Question 3
### Github repo link: https://github.com/jeffweltman/MSDS6306
