---
title: "MSDS6306-Week11-LectureAssignment"
author: "Jeff Weltman"
date: "November 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## *Pulling historical financial data to graphically analyze volatility*

First, we'll pull in some historical financial data for the S&P 500.
```{r Pull historical financial data, echo=TRUE}
library(tseries)
## S&P 500 (^GSPC)
###    SNP - SNP Real Time Price. Currency in USD
SNPdata <- get.hist.quote('^GSPC',quote="Close")
```

Then we'll calculate the volatility.

```{r volatility calculations, echo=TRUE}
SNPret <- log(lag(SNPdata)) - log(SNPdata)
SNPvol <- sd(SNPret) * sqrt(250) * 100
## Define getVol function for volatility
getVol <- function(d, logrets) {
	var = 0
	lam = 0
	varlist <- c()

	for (r in logrets) {
		lam = lam*(1 - 1/d) + 1
	  var = (1 - 1/lam)*var + (1/lam)*r^2
		varlist <- c(varlist, var)
	}

	sqrt(varlist)
}
# Calculate volatility over entire length of series for various three different decay factors: 10 30. 100
volest <- getVol(10,SNPret)
volest2 <- getVol(30,SNPret)
volest3 <- getVol(100,SNPret)
```

Lastly, we'll generate a plot with decay factor 10 and overlay two lines - a red line for decay factor 30 and a blue line for decay factor 100.

```{r Plotting volatility and decay factors, echo=TRUE}
# Plot the results, overlaying the volatility curves on the data, just as was done in the S&P example.
plot(volest,type="l", ylab="Volatility", main="Historical Volatility of the S&P 500")
lines(volest2,type="l", col="red")
lines(volest3,type="l", col="blue")
